Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: todos
Update figures for new query results
paper: temporary caption and paragraph explaining count stuff

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced
    from~\acsbaseresulthours~to~\acsimputedbzeroresult.}

@@

\begin{table}
\todo{extend this table to have counts with new results}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Queries optimized for quality ($\alpha=0$) generally achieve
    lower error than queries optimized for efficiency ($\alpha=1$).}
\label{table:smape}
\end{table}

@@

\todobox{Jose: I'm not a fan of this line, I would remove}{Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.}

>>>>

\begin{table*}
\todo{update this with final queries}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

@@

\begin{figure}
\todo{Relabel 9 somehow, since it is no longer in table of queries but in lined later}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar_13.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced
    from~\acsbaseresulthours~to~\acsimputedbzeroresult.}

@@

We also calculate SMAPE over the number of tuples used to produce the results
in each configuration with respect to the number of tuples satisfying the same query when
the base tables have been imputed. In many cases where the SMAPE reduction between $\alpha = 1$ and
$\alpha = 0$ is small, for example \Cref{q6}, we highlight that the count of tuples can be significantly different between
the two scenarios. So while the aggregate used might not have been significantly affected by the different population,
other aggregates may well be. This highlights a challenge for a user handling data imputation traditionally: it is unclear if
the missing data will have a large or small negative impact on their analysis until they have paid the cost of
running it. By using \ProjectName{} this cost can be lowered significantly.

\begin{table}
\todo{extend this table to have counts with new results}
\centering
\input{tables/perf_summary_13.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Queries optimized for quality ($\alpha=0$) generally achieve
    lower error than queries optimized for efficiency ($\alpha=1$). Count values reflect the SMAPE over the number of tuples
    used for each configuration with respect to the number of tuples used when executing the query after base table imputation. A higher
    count difference reflects more potential for errors.}
\label{table:smape}
\end{table}

@@

%\todobox{Jose: I'm not a fan of this line, I would remove}{Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.}
